Casting Multiple Shadows: High-Dimensional Interactive Data Visualisation with Tours and Embeddings

### 2020-12-11 liminal.Rmd
add arxiv version

```{r setup-videos, cache = FALSE, echo = FALSE}
vid_lookup <- tibble::tribble(
  ~key, ~url, ~path,
  "gaussian",  "https://player.vimeo.com/video/439635921", here::here("img", "liminal-screenshot-gaussian.png"),
  "hierarchical", "https://player.vimeo.com/video/439635905", here::here("img", "liminal-screenshot-hierarchical.png"),
  "trees-01", "https://player.vimeo.com/video/439635892", here::here("img", "liminal-screenshot-trees-01.png"),
  "trees-02", "https://player.vimeo.com/video/439635863", here::here("img", "liminal-screenshot-trees-02.png"),
  "mouse-01", "https://player.vimeo.com/video/439635812", here::here("img", "liminal-screenshot-mouse-01.png"),
  "mouse-02", "https://player.vimeo.com/video/439635843", here::here("img", "liminal-screenshot-mouse-02.png")
)

@@

```{r fake-trees, echo = FALSE, fig.align = "center", fig.cap="(ref:fake-trees)"}
knitr::include_graphics(here::here("img", "tree-view.png"))
```

>>>>

```{r setup-videos, cache = FALSE, echo = FALSE}
vid_lookup <- tibble::tribble(
  ~key, ~url, ~path,
  "gaussian",  "https://player.vimeo.com/video/439635921", "./img/liminal-screenshot-gaussian.png",
  "hierarchical", "https://player.vimeo.com/video/439635905", "./img/liminal-screenshot-hierarchical.png",
  "trees-01", "https://player.vimeo.com/video/439635892", "./img/liminal-screenshot-trees-01.png",
  "trees-02", "https://player.vimeo.com/video/439635863","./img/liminal-screenshot-trees-02.png",
  "mouse-01", "https://player.vimeo.com/video/439635812","img/liminal-screenshot-mouse-01.png",
  "mouse-02", "https://player.vimeo.com/video/439635843", "./img/liminal-screenshot-mouse-02.png"
)

@@

```{r fake-trees, echo = FALSE, fig.align = "center", fig.cap="(ref:fake-trees)"}
knitr::include_graphics("./img/tree-view.png")
```

### 2020-12-11 liminal.tex
add arxiv version

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{/Users/slee0046/paper-liminal/img/liminal-screenshot-gaussian}

@@

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{/Users/slee0046/paper-liminal/img/liminal-screenshot-hierarchical}

@@

{\centering \includegraphics[width=\textwidth]{/Users/slee0046/paper-liminal/img/tree-view}

@@

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{/Users/slee0046/paper-liminal/img/liminal-screenshot-trees-01}

@@

{\centering \includegraphics[width=\textwidth]{/Users/slee0046/paper-liminal/img/liminal-screenshot-trees-02}

@@

{\centering \includegraphics[width=\textwidth,height=0.9\textheight]{/Users/slee0046/paper-liminal/img/liminal-screenshot-mouse-01}

@@

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{/Users/slee0046/paper-liminal/img/liminal-screenshot-mouse-02}

>>>>

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{./img/liminal-screenshot-gaussian}

@@

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{./img/liminal-screenshot-hierarchical}

@@

{\centering \includegraphics[width=\textwidth]{./img/tree-view}

@@

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{./img/liminal-screenshot-trees-01}

@@

{\centering \includegraphics[width=\textwidth]{./img/liminal-screenshot-trees-02}

@@

{\centering \includegraphics[width=\textwidth,height=0.9\textheight]{img/liminal-screenshot-mouse-01}

@@

{\centering \includegraphics[width=\textwidth,height=0.75\textheight]{./img/liminal-screenshot-mouse-02}
